---
title: "Meta-repository for Turner et al., 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Water storage and release policies for all large reservoirs of conterminous United States**

Sean Turner<sup>1\*</sup>, Jennie Steyaert <sup>2</sup>, Laura Condon <sup>2</sup>, and Nathalie Voisin <sup>1,3</sup>

<sup>1 </sup> Pacific Northwest National Laboratory
<sup>2 </sup> University of Arizona
<sup>3 </sup> University of Washington

\* corresponding author: sean.turner@pnnl.gov


**Journal Article:** [![Generic badge](https://img.shields.io/badge/DOI-10.1016/j.jhydrol.2021.126843-orange.svg)](https://doi.org/10.1016/j.jhydrol.2021.126843)

**Reservoir Operating Policies Dataset:** Inferred Storage Targets and Release Functions `ISTARF-CONUS`: [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4602277.svg)](https://doi.org/10.5281/zenodo.4602277)

### Contributing software

| Model | Version | Repository | DOI |
|-------------|-----|------|----------------------------|
| `starfit` | 0.1.0 | https://github.com/IMMM-SFA/starfit/ | [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4924634.svg)](https://doi.org/10.5281/zenodo.4924634) |

### Data requirements

| Dataset | Version | Link | Supporting article to cite |
|-------------|-----|------|----------------------------|
| Global Reservoir and Dam Database `GRanD` | 1.3 | http://globaldamwatch.org/grand/ | [![Generic badge](https://img.shields.io/badge/DOI-10.1890/100125-orange.svg)](https://doi.org/10.1890/100125) |
| Reservoir Operations for CONUS `ResOpsUS` | 1.0 | [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5367383.svg)](https://doi.org/10.5281/zenodo.5367383) | Steyaert et al., *In Review*, Nature Scientific Data. |


## Reproduce my experiment
In Turner et al., 2021, reservoir operations data from `ResOpsUS` are used to infer the operating policies of different reservoirs. The policy inference code is contained in the `starfit` package.

For this example, you will need to first load some libraries:

```{r, echo = FALSE, message= FALSE}
library(dplyr)
# note: you can install `starfit` using devtools:
# devtools::install_github("IMMM-SFA/starfit")
library(starfit)
```

`ResOpsUS` can be downloaded in full and read into R using `starfit` function `read_reservoir_data()`. Alternatively, the same function can access `ResOpsUS` data directly from Zenodo, saving us the effort of downloading the entire dataset.

```{r}

print("ResOps")
1+1

```









