---
title: "Meta-repository for Turner et al., 2021"
output: 
  html_document: 
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

**Water storage and release policies for all large reservoirs of conterminous United States**

Sean Turner<sup>1\*</sup>, Jennie Steyaert <sup>2</sup>, Laura Condon <sup>2</sup>, and Nathalie Voisin <sup>1,3</sup>

<sup>1 </sup> Pacific Northwest National Laboratory
<sup>2 </sup> University of Arizona
<sup>3 </sup> University of Washington

\* corresponding author: sean.turner@pnnl.gov

----------------------------------------------

**Journal Article:** Turner, S.W., Steyaert, J.C., Condon, L. and Voisin, N., 2021. Water storage and release policies for all large reservoirs of conterminous United States. *Journal of Hydrology*, 603, p.126843. [![Generic badge](https://img.shields.io/badge/DOI-10.1016/j.jhydrol.2021.126843-orange.svg)](https://doi.org/10.1016/j.jhydrol.2021.126843)


**Reservoir Operating Policies Dataset:** `ISTARF-CONUS`: [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4602277.svg)](https://doi.org/10.5281/zenodo.4602277)

----------------------------------------------

### Contributing software

| Model | Version | Repository | DOI |
|-------------|-----|------|----------------------------|
| `starfit` | 0.1.0 | https://github.com/IMMM-SFA/starfit/ | [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4924634.svg)](https://doi.org/10.5281/zenodo.4924634) |

### Data requirements

| Dataset | Version | Link | Supporting article to cite |
|-------------|-----|------|----------------------------|
| Global Reservoir and Dam Database `GRanD` | 1.3 | http://globaldamwatch.org/grand/ | Lehner et al., 2011. *Frontiers in Ecology and the Environment* [![Generic badge](https://img.shields.io/badge/DOI-10.1890/100125-orange.svg)](https://doi.org/10.1890/100125) |
| Reservoir Operations for CONUS `ResOpsUS` | 1.0 | [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5367383.svg)](https://doi.org/10.5281/zenodo.5367383) | Steyaert et al., 2022, *Nature Scientific Data* [![Generic badge](https://img.shields.io/badge/DOI-10.1038/s41597022011347-orange.svg)](https://doi.org/10.1038/s41597-022-01134-7) |


### Example for inferring a reservoir policy using `starfit`
In Turner et al., 2021, reservoir operations data from `ResOpsUS` are used to infer the operating policies of different reservoirs. The policy inference code is contained in the `starfit` package.

For this example, you will need to first load some libraries:

```{r}
library(dplyr)
library(ggplot2)
library(starfit)
# note: you can install `starfit` using devtools:
# devtools::install_github("IMMM-SFA/starfit")
```


**NOTE: `ResOpsUS` is currently under embargo but will be publically available after November 8, 2021. Once these data are open, the `starfit` function `read_reservoir_data()` will allow one to access the data directly using `starfit` function `read_reservoir_data()`.

```{r}
read_reservoir_data(
  "https://raw.githubusercontent.com/IMMM-SFA/starfit/master/inst/extdata/",
  # ^^ a placeholder example record is stored at this site pending ResOpsUS public release
  297) ->
  Libby_res_data

Libby_res_data

Libby_res_data %>%
  ggplot(aes(date, s_MCM)) + geom_line(col = "dodgerblue") +
  theme_classic() +
  labs(y = NULL, x = NULL, title = "Daily Storage (MCM) @ Libby Dam")

```

To convert these time series data into a normal operating range:

```{r}
fit_targets(
  "https://raw.githubusercontent.com/IMMM-SFA/starfit/master/inst/extdata/",
  "../../../IM3/Phase 2/P2 WM data-driven/Data-driven reservoir rules/GRanD_Version_1_3/",
  297
) -> Libby_fitted_targets

# NOR parameters are contained in Libby_fitted_targets:
Libby_fitted_targets
```

That's it. If we want to see what those parameters looked like when converted to storage targets:

```{r}
convert_parameters_to_targets(Libby_fitted_targets$`NSR upper bound`, "upper") -> upper_bound
convert_parameters_to_targets(Libby_fitted_targets$`NSR lower bound`, "lower") -> lower_bound

# join and plot
left_join(upper_bound, lower_bound) %>% 
  ggplot(aes(epiweek)) + geom_ribbon(aes(ymax = upper, ymin = lower), col = "black", fill = "dodgerblue") +
  labs(title = "Normal operating range @ Libby Dam", x = "Week of year", y = "Storage (% of capacity)") +
  theme_classic()
```


